Active Learning for Level Set Estimation

### 2013-07-31 figurefactory/files/voned_cl_20.tex
Many small fixes

\addplot [
color=darkgray,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0.5,-2)
};

\addplot [
color=red,
densely dashed,
line width=2.0pt,
forget plot
]
coordinates{
 (0,1.2)(2,1.2)
};

\addplot [
color=black,
solid,
line width=1.5pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (0.5,2.4902)(0.5,3.026)
};

\node at (axis cs:0.45, 3) [anchor=south west,minimum size=16pt] {$Q_4(\*x_{0.5})$};

>>>>

\addplot [
color=darkgray,
solid,
only marks,
mark=*,
mark size=3.5pt,
forget plot
]
coordinates{
 (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=*,
mark size=3.5pt,
forget plot
]
coordinates{
 (0.5,-2)
};

\addplot [
color=red,
dashed,
line width=2.5pt,
forget plot
]
coordinates{
 (0,1.2)(2,1.2)
};

\addplot [
color=black,
solid,
line width=2pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (1.5,1.7052)(1.5,2.241)
};

\node at (axis cs:1.4, 2.3) [anchor=south west,minimum size=16pt] {\Large$C(1.5)$};

### 2013-07-31 figurefactory/files/voned_cl_21.tex
Many small fixes

\addplot [
color=darkgray,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0.5,-2)
};

\addplot [
color=red,
densely dashed,
line width=2.0pt,
forget plot
]
coordinates{
 (0,1.2)(2,1.2)
};

\addplot [
color=black,
solid,
line width=1.5pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (1.5,1.7052)(1.5,2.241)
};

\node at (axis cs:1.4, 2.3) [anchor=south west,minimum size=16pt] {$Q_4(\*x_{1.5})$};

>>>>

\addplot [
color=darkgray,
solid,
only marks,
mark=*,
mark size=3.5pt,
forget plot
]
coordinates{
 (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=*,
mark size=3.5pt,
forget plot
]
coordinates{
 (0.5,-2)(1.5,-2)
};

\addplot [
color=red,
dashed,
line width=2.5pt,
forget plot
]
coordinates{
 (0,1.2)(2,1.2)
};

\addplot [
color=black,
solid,
line width=2pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (1.5,1.7052)(1.5,2.241)
};

\node at (axis cs:1.4, 2.3) [anchor=south west,minimum size=16pt] {\Large$C(1.5)$};

### 2013-07-31 figurefactory/files/voned_cl_30.tex
Many small fixes

\addplot [
color=darkgray,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0.5,-2)(1.5,-2)
};

\addplot [
color=red,
densely dashed,
line width=2.0pt,
forget plot
]
coordinates{
 (0,1.2)(2,1.2)
};

\addplot [
color=black,
solid,
line width=1.5pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (1,0.2645)(1,0.7996)
};

\node at (axis cs:0.88, -0.4) [anchor=south west,minimum size=16pt] {$Q_4(\*x_1)$};

>>>>

\addplot [
color=darkgray,
solid,
only marks,
mark=*,
mark size=3.5pt,
forget plot
]
coordinates{
 (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=*,
mark size=3.5pt,
forget plot
]
coordinates{
 (0.5,-2)(1.5,-2)
};

\addplot [
color=red,
dashed,
line width=2.5pt,
forget plot
]
coordinates{
 (0,1.2)(2,1.2)
};

\addplot [
color=black,
solid,
line width=2pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (1,0.2645)(1,0.7996)
};

\node at (axis cs:0.88, -0.4) [anchor=south west,minimum size=16pt] {\Large$C(1)$};

### 2013-07-31 figurefactory/files/voned_cl_31.tex
Many small fixes

\addplot [
color=darkgray,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0.5,-2)(1.5,-2)
};

\addplot [
color=red,
densely dashed,
line width=2.0pt,
forget plot
]
coordinates{
 (0,1.2)(2,1.2)
};

\addplot [
color=black,
solid,
line width=1.5pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (1,0.2645)(1,0.7996)
};

\node at (axis cs:0.88, -0.4) [anchor=south west,minimum size=16pt] {$Q_4(\*x_1)$};

>>>>

\addplot [
color=darkgray,
solid,
only marks,
mark=*,
mark size=3.5pt,
forget plot
]
coordinates{
 (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=*,
mark size=3.5pt,
forget plot
]
coordinates{
 (0.5,-2)(1.5,-2)
};

\addplot [
color=locol,
solid,
only marks,
mark=*,
mark size=3.5pt,
forget plot
]
coordinates{
 (1,-2)
};

\addplot [
color=red,
dashed,
line width=2.5pt,
forget plot
]
coordinates{
 (0,1.2)(2,1.2)
};

\addplot [
color=black,
solid,
line width=2pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (1,0.2645)(1,0.7996)
};

\node at (axis cs:0.88, -0.4) [anchor=south west,minimum size=16pt] {\Large$C(1)$};

### 2013-07-31 figurefactory/files/voned_cl_40.tex
Many small fixes

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=2,
xtick={0, 0.5, 1, 1.5, 2},
ymin=-2, ymax=4,
tickwidth=0cm,
]

@@

\addplot [
color=darkgray,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0.5,-2)(1.5,-2)
};

\addplot [
color=locol,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (1,-2)
};

\addplot [
color=red,
densely dashed,
line width=2.0pt,
forget plot
]
coordinates{
 (0,1.2)(2,1.2)
};

\addplot [
color=black,
solid,
line width=1.5pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (1,0.2645)(1,0.7996)
};

\node at (axis cs:0.88, -0.4) [anchor=south west,minimum size=16pt] {$Q_4(\*x_1)$};

>>>>

\begin{axis}[%
tick label style={font=\Large},
label style={font=\Large},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\Large},
xticklabel shift={2pt},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=2,
xtick={0, 0.5, 1, 1.5, 2},
ymin=-2, ymax=4,
tickwidth=0cm,
clip=false
]

@@

\addplot [
color=darkgray,
solid,
only marks,
mark=*,
mark size=3.5pt,
forget plot
]
coordinates{
 (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=*,
mark size=3.5pt,
forget plot
]
coordinates{
 (0.5,-2)(1.5,-2)
};

\addplot [
color=locol,
solid,
only marks,
mark=*,
mark size=3.5pt,
forget plot
]
coordinates{
 (1,-2)
};

\addplot [
color=red,
dashed,
line width=2.5pt,
forget plot
]
coordinates{
 (0,1.2)(2,1.2)
};

\addplot [
color=black,
solid,
line width=2pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (0,-0.1683)(0,3.5848)
};

\addplot [
color=black,
solid,
line width=2pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (2,-0.4448)(2,3.3083)
};

\node at (axis cs:0, -0.8) [anchor=south west,minimum size=16pt] {\Large$C(0)$};

\node at (axis cs:1.78, -1) [anchor=south west,minimum size=16pt] {\Large$C(2)$};

### 2013-07-31 figurefactory/files/voned_cl_41.tex
Many small fixes

\addplot [
color=darkgray,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0,-2)(0.5,-2)(1,-2)(1.5,-2)(2,-2)
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0.5,-2)(1.5,-2)
};

\addplot [
color=locol,
solid,
only marks,
mark=*,
mark size=2.5pt,
forget plot
]
coordinates{
 (1,-2)
};

\addplot [
color=red,
densely dashed,
line width=2.0pt,
forget plot
]
coordinates{
 (0,1.2)(2,1.2)
};

\addplot [
color=black,
solid,
line width=1.5pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (0,-0.1683)(0,3.5848)
};

\addplot [
color=black,
solid,
line width=1.5pt,
mark size=3pt,
mark=-,
forget plot
]
coordinates{
 (2,-0.4448)(2,3.3083)
};

\node at (axis cs:0, -0.8) [anchor=south west,minimum size=16pt] {$Q_4(\*x_0)$};

\node at (axis cs:1.78, -1) [anchor=south west,minimum size=16pt] {$Q_4(\*x_2)$};

>>>>

\addplot [
color=darkgray,
solid,
only marks,
mark=square*,
mark size=3.5pt,
forget plot
]
coordinates{
 %(0,-2)
 %(0.019,-2)
(0.02,-2)(0.03,-2)(0.04,-2)(0.05,-2)(0.06,-2)(0.07,-2)(0.08,-2)(0.09,-2)(0.1,-2)(0.11,-2)(0.12,-2)(0.13,-2)(0.14,-2)(0.15,-2)(0.16,-2)(0.17,-2)(0.18,-2)(0.19,-2)(0.2,-2)(0.21,-2)(0.22,-2)(0.23,-2)(0.24,-2)(0.25,-2)(0.26,-2)(0.27,-2)(0.67,-2)(0.68,-2)(0.69,-2)(0.7,-2)(0.71,-2)(0.72,-2)(0.73,-2)(0.74,-2)(0.75,-2)(0.76,-2)(0.77,-2)(0.78,-2)(0.79,-2)(0.8,-2)(0.81,-2)(0.82,-2)(0.83,-2)(0.84,-2)(0.85,-2)(0.86,-2)(0.87,-2)(0.88,-2)(0.89,-2)(0.9,-2)(0.91,-2)(0.92,-2)(1.1,-2)(1.11,-2)(1.12,-2)(1.13,-2)(1.14,-2)(1.15,-2)(1.16,-2)(1.17,-2)(1.18,-2)(1.19,-2)(1.2,-2)(1.21,-2)(1.22,-2)(1.23,-2)(1.24,-2)(1.25,-2)(1.26,-2)(1.27,-2)(1.28,-2)(1.29,-2)(1.3,-2)(1.31,-2)(1.32,-2)(1.33,-2)(1.34,-2)(1.35,-2)(1.36,-2)(1.37,-2)(1.38,-2)(1.39,-2)(1.4,-2)(1.41,-2)(1.63,-2)(1.64,-2)(1.65,-2)(1.66,-2)(1.67,-2)(1.68,-2)(1.69,-2)(1.7,-2)(1.71,-2)(1.72,-2)(1.73,-2)(1.74,-2)(1.75,-2)(1.76,-2)(1.77,-2)(1.78,-2)(1.79,-2)(1.8,-2)(1.81,-2)(1.82,-2)(1.83,-2)(1.84,-2)(1.85,-2)(1.86,-2)(1.87,-2)(1.88,-2)(1.89,-2)(1.9,-2)(1.91,-2)(1.92,-2)(1.93,-2)(1.94,-2)(1.95,-2)(1.96,-2)(1.97,-2)(1.98,-2)
%(1.981,-2)
 %(2,-2) 
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=square*,
mark size=3.5pt,
forget plot
]
coordinates{
 (0.28,-2)(0.29,-2)(0.3,-2)(0.31,-2)(0.32,-2)(0.33,-2)(0.34,-2)(0.35,-2)(0.36,-2)(0.37,-2)(0.38,-2)(0.39,-2)(0.4,-2)(0.41,-2)(0.42,-2)(0.43,-2)(0.44,-2)(0.45,-2)(0.46,-2)(0.47,-2)(0.48,-2)(0.49,-2)(0.5,-2)(0.51,-2)(0.52,-2)(0.53,-2)(0.54,-2)(0.55,-2)(0.56,-2)(0.57,-2)(0.58,-2)(0.59,-2)(0.6,-2)(0.61,-2)(0.62,-2)(0.63,-2)(0.64,-2)(0.65,-2)(0.66,-2)(1.42,-2)(1.43,-2)(1.44,-2)(1.45,-2)(1.46,-2)(1.47,-2)(1.48,-2)(1.49,-2)(1.5,-2)(1.51,-2)(1.52,-2)(1.53,-2)(1.54,-2)(1.55,-2)(1.56,-2)(1.57,-2)(1.58,-2)(1.59,-2)(1.6,-2)(1.61,-2)(1.62,-2) 
};

\addplot [
color=locol,
solid,
only marks,
mark=square*,
mark size=3.5pt,
forget plot
]
coordinates{
 (0.93,-2)(0.94,-2)(0.95,-2)(0.96,-2)(0.97,-2)(0.98,-2)(0.99,-2)(1,-2)(1.01,-2)(1.02,-2)(1.03,-2)(1.04,-2)(1.05,-2)(1.06,-2)(1.07,-2)(1.08,-2)(1.09,-2) 
};

\addplot [
color=red,
dashed,
line width=2.5pt,
forget plot
]
coordinates{
 (0,1.2)(2,1.2)
};

### 2013-07-31 figurefactory/files/voned_cl_41_amb_2.tex
Most of the changes discussed with Andreas
Many small fixes

\addplot [
color=darkgray,
solid,
only marks,
mark=square*,
mark size=2.5pt,
forget plot
]
coordinates{
 %(0,-2)
 (0.01,-2)(0.02,-2)(0.03,-2)(0.04,-2)(0.05,-2)(0.06,-2)(0.07,-2)(0.08,-2)(0.09,-2)(0.1,-2)(0.11,-2)(0.12,-2)(0.13,-2)(0.14,-2)(0.15,-2)(0.16,-2)(0.17,-2)(0.18,-2)(0.19,-2)(0.2,-2)(0.21,-2)(0.22,-2)(0.23,-2)(0.24,-2)(0.25,-2)(0.26,-2)(0.27,-2)(0.67,-2)(0.68,-2)(0.69,-2)(0.7,-2)(0.71,-2)(0.72,-2)(0.73,-2)(0.74,-2)(0.75,-2)(0.76,-2)(0.77,-2)(0.78,-2)(0.79,-2)(0.8,-2)(0.81,-2)(0.82,-2)(0.83,-2)(0.84,-2)(0.85,-2)(0.86,-2)(0.87,-2)(0.88,-2)(0.89,-2)(0.9,-2)(0.91,-2)(0.92,-2)(1.1,-2)(1.11,-2)(1.12,-2)(1.13,-2)(1.14,-2)(1.15,-2)(1.16,-2)(1.17,-2)(1.18,-2)(1.19,-2)(1.2,-2)(1.21,-2)(1.22,-2)(1.23,-2)(1.24,-2)(1.25,-2)(1.26,-2)(1.27,-2)(1.28,-2)(1.29,-2)(1.3,-2)(1.31,-2)(1.32,-2)(1.33,-2)(1.34,-2)(1.35,-2)(1.36,-2)(1.37,-2)(1.38,-2)(1.39,-2)(1.4,-2)(1.41,-2)(1.63,-2)(1.64,-2)(1.65,-2)(1.66,-2)(1.67,-2)(1.68,-2)(1.69,-2)(1.7,-2)(1.71,-2)(1.72,-2)(1.73,-2)(1.74,-2)(1.75,-2)(1.76,-2)(1.77,-2)(1.78,-2)(1.79,-2)(1.8,-2)(1.81,-2)(1.82,-2)(1.83,-2)(1.84,-2)(1.85,-2)(1.86,-2)(1.87,-2)(1.88,-2)(1.89,-2)(1.9,-2)(1.91,-2)(1.92,-2)(1.93,-2)(1.94,-2)(1.95,-2)(1.96,-2)(1.97,-2)(1.98,-2)(1.99,-2)
 %(2,-2) 
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=square*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0.28,-2)(0.29,-2)(0.3,-2)(0.31,-2)(0.32,-2)(0.33,-2)(0.34,-2)(0.35,-2)(0.36,-2)(0.37,-2)(0.38,-2)(0.39,-2)(0.4,-2)(0.41,-2)(0.42,-2)(0.43,-2)(0.44,-2)(0.45,-2)(0.46,-2)(0.47,-2)(0.48,-2)(0.49,-2)(0.5,-2)(0.51,-2)(0.52,-2)(0.53,-2)(0.54,-2)(0.55,-2)(0.56,-2)(0.57,-2)(0.58,-2)(0.59,-2)(0.6,-2)(0.61,-2)(0.62,-2)(0.63,-2)(0.64,-2)(0.65,-2)(0.66,-2)(1.42,-2)(1.43,-2)(1.44,-2)(1.45,-2)(1.46,-2)(1.47,-2)(1.48,-2)(1.49,-2)(1.5,-2)(1.51,-2)(1.52,-2)(1.53,-2)(1.54,-2)(1.55,-2)(1.56,-2)(1.57,-2)(1.58,-2)(1.59,-2)(1.6,-2)(1.61,-2)(1.62,-2) 
};

\addplot [
color=locol,
solid,
only marks,
mark=square*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0.93,-2)(0.94,-2)(0.95,-2)(0.96,-2)(0.97,-2)(0.98,-2)(0.99,-2)(1,-2)(1.01,-2)(1.02,-2)(1.03,-2)(1.04,-2)(1.05,-2)(1.06,-2)(1.07,-2)(1.08,-2)(1.09,-2) 
};

\addplot [
color=red,
densely dashed,
line width=2.0pt,
forget plot
]
coordinates{
 (0,1.2)(2,1.2)
};

\addplot [
color=black,
solid,
line width=1.5pt,
mark=-,
mark size=3pt,
forget plot
]
coordinates{
 (1.23,0.0268)(1.23,1.9195)
};

@@

\addplot [
color=black,
solid,
line width=1.5pt,
mark=-,
mark size=3pt,
forget plot
]
coordinates{
 (0.23,0.9288)(0.23,3.8259)
};

>>>>

\addplot [
color=darkgray,
solid,
only marks,
mark=square*,
mark size=3.5pt,
forget plot
]
coordinates{
 %(0,-2)
 %(0.019,-2)
(0.02,-2)(0.03,-2)(0.04,-2)(0.05,-2)(0.06,-2)(0.07,-2)(0.08,-2)(0.09,-2)(0.1,-2)(0.11,-2)(0.12,-2)(0.13,-2)(0.14,-2)(0.15,-2)(0.16,-2)(0.17,-2)(0.18,-2)(0.19,-2)(0.2,-2)(0.21,-2)(0.22,-2)(0.23,-2)(0.24,-2)(0.25,-2)(0.26,-2)(0.27,-2)(0.67,-2)(0.68,-2)(0.69,-2)(0.7,-2)(0.71,-2)(0.72,-2)(0.73,-2)(0.74,-2)(0.75,-2)(0.76,-2)(0.77,-2)(0.78,-2)(0.79,-2)(0.8,-2)(0.81,-2)(0.82,-2)(0.83,-2)(0.84,-2)(0.85,-2)(0.86,-2)(0.87,-2)(0.88,-2)(0.89,-2)(0.9,-2)(0.91,-2)(0.92,-2)(1.1,-2)(1.11,-2)(1.12,-2)(1.13,-2)(1.14,-2)(1.15,-2)(1.16,-2)(1.17,-2)(1.18,-2)(1.19,-2)(1.2,-2)(1.21,-2)(1.22,-2)(1.23,-2)(1.24,-2)(1.25,-2)(1.26,-2)(1.27,-2)(1.28,-2)(1.29,-2)(1.3,-2)(1.31,-2)(1.32,-2)(1.33,-2)(1.34,-2)(1.35,-2)(1.36,-2)(1.37,-2)(1.38,-2)(1.39,-2)(1.4,-2)(1.41,-2)(1.63,-2)(1.64,-2)(1.65,-2)(1.66,-2)(1.67,-2)(1.68,-2)(1.69,-2)(1.7,-2)(1.71,-2)(1.72,-2)(1.73,-2)(1.74,-2)(1.75,-2)(1.76,-2)(1.77,-2)(1.78,-2)(1.79,-2)(1.8,-2)(1.81,-2)(1.82,-2)(1.83,-2)(1.84,-2)(1.85,-2)(1.86,-2)(1.87,-2)(1.88,-2)(1.89,-2)(1.9,-2)(1.91,-2)(1.92,-2)(1.93,-2)(1.94,-2)(1.95,-2)(1.96,-2)(1.97,-2)(1.98,-2)
%(1.981,-2)
 %(2,-2) 
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=square*,
mark size=3.5pt,
forget plot
]
coordinates{
 (0.28,-2)(0.29,-2)(0.3,-2)(0.31,-2)(0.32,-2)(0.33,-2)(0.34,-2)(0.35,-2)(0.36,-2)(0.37,-2)(0.38,-2)(0.39,-2)(0.4,-2)(0.41,-2)(0.42,-2)(0.43,-2)(0.44,-2)(0.45,-2)(0.46,-2)(0.47,-2)(0.48,-2)(0.49,-2)(0.5,-2)(0.51,-2)(0.52,-2)(0.53,-2)(0.54,-2)(0.55,-2)(0.56,-2)(0.57,-2)(0.58,-2)(0.59,-2)(0.6,-2)(0.61,-2)(0.62,-2)(0.63,-2)(0.64,-2)(0.65,-2)(0.66,-2)(1.42,-2)(1.43,-2)(1.44,-2)(1.45,-2)(1.46,-2)(1.47,-2)(1.48,-2)(1.49,-2)(1.5,-2)(1.51,-2)(1.52,-2)(1.53,-2)(1.54,-2)(1.55,-2)(1.56,-2)(1.57,-2)(1.58,-2)(1.59,-2)(1.6,-2)(1.61,-2)(1.62,-2) 
};

\addplot [
color=locol,
solid,
only marks,
mark=square*,
mark size=3.5pt,
forget plot
]
coordinates{
 (0.93,-2)(0.94,-2)(0.95,-2)(0.96,-2)(0.97,-2)(0.98,-2)(0.99,-2)(1,-2)(1.01,-2)(1.02,-2)(1.03,-2)(1.04,-2)(1.05,-2)(1.06,-2)(1.07,-2)(1.08,-2)(1.09,-2) 
};

\addplot [
color=red,
dashed,
line width=2.5pt,
forget plot
]
coordinates{
 (0,1.2)(2,1.2)
};

\addplot [
color=black,
solid,
line width=2pt,
mark=-,
mark size=3pt,
forget plot
]
coordinates{
 (1.23,0.0268)(1.23,1.9195)
};

@@

\addplot [
color=black,
solid,
line width=2pt,
mark=-,
mark size=3pt,
forget plot
]
coordinates{
 (0.23,0.9288)(0.23,3.8259)
};

\addplot [
color=yellow,
solid,
line width=4pt,
forget plot
]
coordinates{
 (0.23,0.9288)(0.23,1.2)
};

### 2013-07-31 figurefactory/files/voned_cl_41_amb_poster.tex
Many small fixes

\begin{axis}[%
tick label style={font=\Huge},
label style={font=\Huge},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\Huge},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=2,
xtick={0, 0.5, 1, 1.5, 2},
ymin=-2, ymax=4,
tickwidth=0cm,
]

@@

\addplot [
color=black,
dotted,
line width=2.5pt,
forget plot
]
coordinates{
 (1,-2)(1,0.5)
};

\addplot [
color=black,
dotted,
line width=2.5pt,
forget plot
]
coordinates{
 (1.5,-2)(1.5,2)
};

\addplot [
color=black,
dotted,
line width=2.5pt,
forget plot
]
coordinates{
 (0.5,-2)(0.5,2.8)
};

\addplot [
color=black,
only marks,
mark=*,
mark size=2.5pt,
line width=2.0pt,
forget plot
]
coordinates{
 (0.5,-2)(1,-2)(1.5,-2)
};

\addplot [
color=black,
only marks,
mark=x,
mark size=7.5pt,
line width=2.5pt,
forget plot
]
coordinates{
 (0.5,2.8)(1,0.5)(1.5,2)
};

>>>>

\begin{axis}[%
tick label style={font=\Huge},
label style={font=\Huge},
label shift={-4pt},
xlabel shift={-6pt},
xticklabel shift={5pt},
legend style={font=\Huge},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=2,
xtick={0, 0.5, 1, 1.5, 2},
ymin=-2, ymax=4,
tickwidth=0cm,
]

@@

\addplot [
color=darkgray,
solid,
only marks,
mark=square*,
mark size=5pt,
forget plot
]
coordinates{
 %(0,-2)
 %(0.01,-2)
(0.023,-2)
(0.03,-2)(0.04,-2)(0.05,-2)(0.06,-2)(0.07,-2)(0.08,-2)(0.09,-2)(0.1,-2)(0.11,-2)(0.12,-2)(0.13,-2)(0.14,-2)(0.15,-2)(0.16,-2)(0.17,-2)(0.18,-2)(0.19,-2)(0.2,-2)(0.21,-2)(0.22,-2)(0.23,-2)(0.24,-2)(0.25,-2)(0.26,-2)(0.27,-2)(0.67,-2)(0.68,-2)(0.69,-2)(0.7,-2)(0.71,-2)(0.72,-2)(0.73,-2)(0.74,-2)(0.75,-2)(0.76,-2)(0.77,-2)(0.78,-2)(0.79,-2)(0.8,-2)(0.81,-2)(0.82,-2)(0.83,-2)(0.84,-2)(0.85,-2)(0.86,-2)(0.87,-2)(0.88,-2)(0.89,-2)(0.9,-2)(0.91,-2)(0.92,-2)(1.1,-2)(1.11,-2)(1.12,-2)(1.13,-2)(1.14,-2)(1.15,-2)(1.16,-2)(1.17,-2)(1.18,-2)(1.19,-2)(1.2,-2)(1.21,-2)(1.22,-2)(1.23,-2)(1.24,-2)(1.25,-2)(1.26,-2)(1.27,-2)(1.28,-2)(1.29,-2)(1.3,-2)(1.31,-2)(1.32,-2)(1.33,-2)(1.34,-2)(1.35,-2)(1.36,-2)(1.37,-2)(1.38,-2)(1.39,-2)(1.4,-2)(1.41,-2)(1.63,-2)(1.64,-2)(1.65,-2)(1.66,-2)(1.67,-2)(1.68,-2)(1.69,-2)(1.7,-2)(1.71,-2)(1.72,-2)(1.73,-2)(1.74,-2)(1.75,-2)(1.76,-2)(1.77,-2)(1.78,-2)(1.79,-2)(1.8,-2)(1.81,-2)(1.82,-2)(1.83,-2)(1.84,-2)(1.85,-2)(1.86,-2)(1.87,-2)(1.88,-2)(1.89,-2)(1.9,-2)(1.91,-2)(1.92,-2)(1.93,-2)(1.94,-2)(1.95,-2)(1.96,-2)(1.97,-2)
(1.977,-2)
%(1.99,-2)
 %(2,-2) 
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=square*,
mark size=5pt,
forget plot
]
coordinates{
 (0.28,-2)(0.29,-2)(0.3,-2)(0.31,-2)(0.32,-2)(0.33,-2)(0.34,-2)(0.35,-2)(0.36,-2)(0.37,-2)(0.38,-2)(0.39,-2)(0.4,-2)(0.41,-2)(0.42,-2)(0.43,-2)(0.44,-2)(0.45,-2)(0.46,-2)(0.47,-2)(0.48,-2)(0.49,-2)(0.5,-2)(0.51,-2)(0.52,-2)(0.53,-2)(0.54,-2)(0.55,-2)(0.56,-2)(0.57,-2)(0.58,-2)(0.59,-2)(0.6,-2)(0.61,-2)(0.62,-2)(0.63,-2)(0.64,-2)(0.65,-2)(0.66,-2)(1.42,-2)(1.43,-2)(1.44,-2)(1.45,-2)(1.46,-2)(1.47,-2)(1.48,-2)(1.49,-2)(1.5,-2)(1.51,-2)(1.52,-2)(1.53,-2)(1.54,-2)(1.55,-2)(1.56,-2)(1.57,-2)(1.58,-2)(1.59,-2)(1.6,-2)(1.61,-2)(1.62,-2) 
};

\addplot [
color=locol,
solid,
only marks,
mark=square*,
mark size=5pt,
forget plot
]
coordinates{
 (0.93,-2)(0.94,-2)(0.95,-2)(0.96,-2)(0.97,-2)(0.98,-2)(0.99,-2)(1,-2)(1.01,-2)(1.02,-2)(1.03,-2)(1.04,-2)(1.05,-2)(1.06,-2)(1.07,-2)(1.08,-2)(1.09,-2) 
};

\addplot [
color=red,
dashed,
line width=3.0pt,
forget plot
]
coordinates{
 (0,1.2)(2,1.2)
};

\addplot [
color=black,
solid,
line width=3pt,
mark=-,
mark size=4pt,
forget plot
]
coordinates{
 (1.23,0.0268)(1.23,1.9195)
};

\addplot [
color=yellow,
solid,
line width=5pt,
forget plot
]
coordinates{
 (1.23,1.2)(1.23,1.9195)
};

\addplot [
color=black,
solid,
line width=3pt,
mark=-,
mark size=4pt,
forget plot
]
coordinates{
 (0.23,0.9288)(0.23,3.8259)
};

\addplot [
color=yellow,
solid,
line width=5pt,
forget plot
]
coordinates{
 (0.23,0.9288)(0.23,1.2)
};
